Trajectory Mapping Results

### 2021-03-22 scripts/analyze_trajectories.Rmd
dynamic title traj report

---
title: "Trajectory Mapping Results"
subtitle: "Analysis Europe10 300 particles"
author: "Cecilia Valenzuela"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  beamer_presentation:
    theme: "Pittsburgh"
    colortheme: "dove"
    fonttheme: "structurebold"
    highlight: pygments
classoption: "aspectratio=169"
fontsize: 8pt
tables: yes
---

```{r parser, echo = FALSE}
library(tidyverse)
# Parser -----------------------------------------------------------------------
argsR <- commandArgs(TRUE)
args_list = str_split(paste(argsR, collapse=""), pattern="--")
args_llist = lapply(args_list, function(x) str_split(x, pattern="="))
argsDF = as.data.frame(do.call("rbind", args_llist[[1]]))
args <- as.list(as.character(argsDF$V2))
names(args) <- argsDF$V1
args$burnin = as.integer(args$burnin)
args$n = as.integer(args$n)
```

>>>>

---
title: "Trajectory Mapping Results"
author: "Cecilia Valenzuela"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  beamer_presentation:
    theme: "Pittsburgh"
    colortheme: "dove"
    fonttheme: "structurebold"
    highlight: pygments
classoption: "aspectratio=169"
fontsize: 8pt
tables: yes
---

```{r parser, echo = FALSE}
library(tidyverse)
# Parser -----------------------------------------------------------------------
argsR <- commandArgs(TRUE)
args_list <- str_split(paste(argsR, collapse=""), pattern="--")
args_llist <- lapply(args_list, function(x) str_split(x, pattern="="))
argsDF <- as.data.frame(do.call("rbind", args_llist[[1]]))
args <- as.list(as.character(argsDF$V2))
names(args) <- argsDF$V1
args$burnin <- as.integer(args$burnin)
args$n <- as.integer(args$n)
title <- paste("Analysis", gsub("\\.", " ", gsub(".TL.traj", " particles", str_split(args$args, "/")[[1]][3])))
```

---
subtitle: "`r title`"
---
